---
title: "Introduction to openFoodwrappeR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to openFoodwrappeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

A wrapper in R for the [Open Food Facts](https://world.openfoodfacts.org/) API.

```{r setup}
library(openFoodwrappeR)
```

# Retrieving a product

## Intuitive method

In order to retrieve a product based a search term, use the `product()` function:

```{r}
x = product('hot sauce')
class(x)
length(x$product)
```

This function returns the parsed `.json` information as a list.

If `R` was running in interactive mode, the user would be prompted to enter a number in order to select which product they would like from the printed list. 


## Get product numbers

If you want to get product numbers, you can use the `search_by_name` function:

```{r}
y = search_by_name('milk chocolate')
y
```


## Search by product number

If you already have a product number and want to retrieve information using the exact product number, use the `product_by_prodnum` function:

```{r}
z = product_by_prodnum('80310891')
class(z)
length(z$product)
```


# Retrieving information from a product


## Carbon footprint

```{r}
#carbon_footprint(x)
#plot_carbon(list(x, z))
```




## Allergens


```{r}
#view_allergens(x)
```




# Comparing multiple products

text



# Plotting

text

