---
title: "Introduction to openFoodwrappeR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to openFoodwrappeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

A wrapper in R for the [Open Food Facts](https://world.openfoodfacts.org/) API.

```{r setup}
library(openFoodwrappeR)
```

# Retrieving a product

## Intuitive method

In order to retrieve a product based a search term, use the `product()` function:

```{r}
y = product('kale smoothie', num=4)
x = product('nutella', num=3) 
class(x)
length(x$product)
```

This function returns the parsed `.json` information as a list.

If `R` was running in interactive mode (or if you do not pass `num`), the user would be prompted to enter a number in order to select which product they would like from the printed list. 


## Get product numbers

If you want to get product numbers, you can use the `search_by_name` function:

```{r}
lst = search_by_name('milk chocolate')
lst
```


## Search by product number

If you already have a product number and want to retrieve information using the exact product number, use the `product_by_prodnum` function:

```{r}
z = product_by_prodnum('3168930010906')
class(z)
length(z$product)
```


# Retrieving information from a product

## Product Name 

```{r}
prod_name(x)
prod_name(y)
prod_name(z)
```


## Food group

```{r}
food_group(x)
food_group(y)
food_group(z)
```



## Carbon footprint

```{r}
carbon_footprint(x)
carbon_footprint(y)
carbon_footprint(z)
```


## Sugar (per 100g)

```{r}
sugar_per_100g(x)
sugar_per_100g(y)
sugar_per_100g(z)
```



## Allergens


```{r}
view_allergens(x)
view_allergens(y)
view_allergens(z)
```




# Plotting


## Carbon footprint

```{r, fig.width=8}
plot_carbon(list(x, y, z))
```


## Sugar (per 100g)

```{r, fig.width=8}
plot_sugar(list(x, y, z))
```

